Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-09-25 text/paper/reviews_2/response_letter.md

# Response to editor and reviewer comments

The main changes from the previous version are:

1. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions; concretely:
	a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
	c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.
2. shortening of section 3 to remove unnecessary detail in predictions of "core theories"
3. addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments, which made clear that the previous version may not have made the motivation of our design sufficiently clear

@@

## Editor comments

> I would like to ask two things of you: 
>
> (1) have a good think about the balanced conclusion you draw (the data are hard for both sides of the theoretical divide --- reviewer 2: the data clearly favours grammaticalism) and address the reviewer's worry as good as you can (s/he can't be the only one interpreting your paper like that);

We agree that our previous version has not been ideally clear on this. It is not our intention to polarize by misleading rhetorics. We have tried to make very clear in the current version that our main conclusions from our data are (as already stated above):

a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.

@@

> (2) rethink the value of the fine-grained description of the landscape of theoretical options (section 3.1/3.2).

Although we had thought that it would be good for the readers to see the full space of possible predictions about preference patterns that relevant "core theories" + "auxiliary hypotheses" give, we agree that it is not strictly necessary to introduce all of these distinctions. We have therefore removed those chunks of Section 3 which are not strictly relevant for late discussions (including Table 2, which summarized the predictions). Some particular "auxiliary assumptions" are taken up in the discussion section 6, but only those that are relevant for the overall discussion, like Magri's appeal to obligatory exhaustification, which is an example for how grammaticalism could predict our data.

@@

## Reviewer 2

Reviewer 2 actually raises many points, not all of which are fully clear to us. We tried our very best to address all of the issues raised (insofar as we understood what was asked of us), but paid particular attention to those issues flagged as most important by the reviewer herself/himself or the editor.

[In the following, we reproduce the full review and use boldface to indicate the aspects that subsequent comments target.]

>The authors have done a good job responding to the first round of feedback. As in the previous round of review, I believe the paper makes a valuable contribution to the literature on scalar strengthening, and that the paper should be published. However, I continue to believe there is room for improvement. Specifically, **I believe the paper can be streamlined by taking fuller advantage of previous results**, which I hope will also clarify the contributions that the paper makes. 
>
>My most important comment, which I'll try to spell out in Section 1 below, is that the question-answer structure of the paper does not come across as cleanly as it should. **To my mind, the paper aims to answer two questions: (i) Are embedded strengthenings licensed only under marked prosody, i.e., is the Prosodic Marking Hypothesis true? (ii) Are there preferences for the different readings predicted by theories of strengthening? If so, what are they, and how are they determined?** 
>
> I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis). Concerning question (ii), the paper leaves it unresolved, which would be fine had the authors not mischaracterized the question by invoking the Strongest Meaning Hypothesis in the way that they did (as I hope to clarify below). If these issues could be resolved in a revised version, I would have no serious objection to publication.

We feel that this description of what the paper is about is unfortunately not entirely correct. This could lead to certain misunderstandings, so we clarify our position here. We have also added to the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and motivation for what we are doing. (It is our fault, of course, that this has not been sufficiently clear in the previous version.)

One of our main goals in this paper is, indeed, to address the effects of prosody, but with a particular motivation, namely to rule out effects of "silent prosody" as confounds in the interpretation of earlier data. This is important because all previous experimental results that depend on visual presentation of sentences could, in principle, be subject to doubt if we hypothesize (like many do) that prosody plays a role in this domain. This also includes the results of Chemla & Spector. This is why we want to be more careful in this paper and not take for granted the conclusions of Chemla & Spector contrary to what the reviewer suggests we should do.

Our reluctance to accept Chemla & Spector's conclusions also comes from the recent critique of, in particular, Bart Geurts and Bob van Tiel, who argue that Chemla & Spector's results could be influenced unduly by pictorial effects. This is the main motivation for our incremental verification task, as argued in Section 4.4 and followed up in the reflection section 6.

In effect, the main point of our paradigm is that we would not want to take "full advantage of previous results" but (given the published criticism of these) take a careful reassessment and a novel experimental approach. We hope that by adding few strategically placed elements of emphasis and explanation (introduction, sections 4 & 6) this will become more transparent.

<!---Unfortunately, we do not understand in what sense the paper leaves question (ii) unresolved, according to the reviewer. To be clear on this, we wanted to get experimental evidence for preferences among putative readings, and we did. We also discuss whether these are predicted by the competing theories. We have adjusted the formulation of these conclusions according to the reviewer's well-taken suggestions in the new version (see below). We never meant to address the question how preferences are determined (and are not clear on what this should mean).-->

>
>
>Section 1: The question-answer structure of the paper
>
>It will help me to discuss the paper's contributions by taking Chemla & Spector (2011, hf. CS) as relevant background, as they also aimed to detect embedded readings in AS and ES sentences and found results that are sometimes supported but sometimes challenged by the present authors. I focus here on ES sentences, in part because AS sentences are not ideal for teasing apart "grammaticalism" from "unrestricted traditionalism", for reasons discussed in CS and elsewhere. My aim here is to identify some of the important empirical results from the current paper, and to relate them to questions (i) and (ii) above:
>
>Empirical Result (1): Like CS, but using a different method, the present authors find that embedded strengthenings are available.
>
>Consequences of (1): This result supports two of CS's claims. First, it provides further evidence for embedded strengthening (and hence, on the face of it, against Traditionalism -- pending further clarification of "typicality"), though of course it leaves open the question in (i) above. Second, **(1) provides further support for CS's claim that the Strongest Meaning Hypothesis is probably *not* the right disambiguation principle (see note 6 of CS, and CS's section 5.5.2)**.

We are very grateful for drawing our attention to the fact that we should mention that Chemla & Spector have already discussed their data as countering the Strongest Meaning Hypothesis. Our position to this is that, yes, we provide further evidence, but also further evidence that is relevant, given the doubts that were brought forth against Chemla & Spector's design and interpretation and the additional doubts that arise from issues with "silent prosody".

<!--There must be some misunderstanding here (see also above): the incremental verification task is motivated by worries about potential pictorial effects. This is orthogonal to the issue of "silent prosody".-->

> Empirical Result (2): The present authors find that embedded strengthenings are available independent of prosodic marking. This result is totally new, and is made possible by their new method (their Incremental Verification Task).
>
> Consequences of (2): This result argues against the Prosodic Marking Hypothesis (cf. question (i) above).
> 
> (3) Empirical Result (3): The present authors find that the literal reading is preferred to the local reading, which is in stark opposition with what CS found. 
>
>Consequences of (3): Given the discussion in (1) above, an obvious challenge is to explain what might have led to different preferences in CS's sample and the one in the present paper (cf. question (ii) above).
>
> If my reading of the paper is correct, then several changes to the paper are in order. 
>
>   - First, I believe **much of the discussion in section 3 concerning auxiliary assumptions should be shortened or even deleted entirely.** To begin with, much of the discussion about Traditionalism seems irrelevant to me. The really important assumption here is the Prosodic Marking Hypothesis, which can be simply stated without bothering with the distinction between weak/strong and restricted/unrestricted traditionalism. In fact, so far as I can tell, nothing that the authors say later in the paper bears on these differences, in part because traditionalism qua core theory is inconsistent with the authors' results. Turning to grammaticalism, in light of the fact that **the Strongest Meaning Hypothesis was already argued in CS to be inoperative (or at least, not dominant) in ES sentences, the authors' decision to take that as the most promising example of a disambiguation criterion seems unjustified.** In sum, the authors introduce many discourse referents in section 3 corresponding to possible combinations of core theory + auxiliary assumptions (all the variants of traditionalism and the conjunction of grammaticalism and the SMH), and at the end of the paper we are reminded that CS already gave us reason to reject them all. This is not very cooperative.   
>   **My concrete suggestion is to considerably shorten Section 3 by not getting into all the choice points concerning Traditionalism (weak/strong, restricted/unrestricted) or Grammaticalism (Magri/QUD/SMH). All of these are irrelevant to the Prosodic Marking Hypothesis, and in any event nothing new is discovered by paper's end about the right auxiliary assumptions**, other than that the answer is unlikely to be straightforward (cf. the conflict with CS's results alluded to above).

@@

We have taken up the suggestion to shorten Section 3 in the way that the reviewer describes.

On the other hand, for the very reasons described above, we are reluctant to accept the results and conclusions of Chemla & Spector as given. Since our design was motivated by catering to the very problems raised for Chemla & Spector, we do believe that our data gives new and interesting information about preference of readings. This is also because, as we argue in Section 4.4, we explicitly compare data from embedded scalars with other ambiguous constructions in the very same experiment (same method, same subject pool).

> - Second, the authors' abstract and the discussion in the paper make it clear that there are challenges for both traditionalism and grammaticalism. This is very important, but **the authors' discussion makes it seem as though the challenges for the two approaches are more on a par than they actually are. Traditionalism (as a core theory) is inconsistent with the authors' data, and grammaticalism (as a core theory) is consistent with their data**. Of course, grammaticalism is still in need of auxiliary assumptions to account for the data about preferences, but this should occasion no surprise. For example, last I checked the psycholinguistics community was still trying to figure out, say, how PP-attachment ambiguities are resolved; just because we don't know how, this does not lead anyone to suggest that syntactic theories that generate PP-attachment ambiguities are in need of "refinement", does it?    
>   My concrete suggestion is to **rephrase the abstract and other relevant passages in the paper so that it does not misleadingly suggest that grammaticalism qua core theory faces any particular difficulty with the authors' results**; what is missing here is a theory of preference, but this is needed for any theoretical approach to strengthening. For note that the discrepancy between CS's findings and the present authors' findings concerning preferences need to be accounted for one way or another; since this is a problem for everyone, I don't think it is fair to single out grammaticalism as being in need of refinement, at least not until it is shown that some other approach predicts the discrepancy between CS and the present authors' data on preferences.

We agree that our previous version did not make this clear enough. We reformulated relevant locations to make clear what our position is, namely (same as above):

	a. we stress (even more than before) that grammaticalism qua "core theory" is compatible with our data, while traditionalism is not; 
	b. still, we maintain that grammaticalism qua "core theory" is *trivially* compatible with our data, because it would not be inconsistent with any possible outcome of our experiment; 
	c. the only auxiliary assumption for grammaticalism that is directly applicable to our experiment (selecting reading preferences in terms of logical strength alone) is not compatible with our data.

> Section 2: Minor comments/thoughts (feel free to ignore)
>
> A: "Exactly one" as monotonic: **The authors suggest, based on the "true" responses at Step 2, that some of their participants might have re-interpreted "exactly one" as "at least one." I'm wondering if there is a less radical way to make sense of their participants' behaviour: for what it's worth, my intuition is that there might be domain-restriction effects here.** There is exactly one uncovered bell at Step 2; thus, the sentence is literally true under a reading in which the domain of the quantifier is restricted to this one individual. I'm not exactly sure how to dissociate this suggestion from the authors', and I of course wouldn't insist that the authors do this. I raise the idea here simply for their consideration. With this in mind, in future work perhaps the authors might consider examining what would happen if Step 1 were followed instead by what is currently Step 3. The domain-restriction proposal would predict less "true" responses here because now there are two bells that are salient in the domain, but an "at least one" reading would still easily permit a "true" response here. (Note that getting rid of the current Step 2 is largely harmless, since global readings were basically absent in this paradigm.)

This is a good and interesting suggestion. We cannot follow up on this in the paper, but acknowledge the point in a footnote.

> B: The Strongest Meaning Hypothesis, Again: **As I noted earlier, it does not seem appropriate to assume the SMH for this paradigm in light of CS's results and discussion.** However, I should like to add that one has to be careful about what the SMH actually states when we consider exhaustification, and here perhaps CS themselves could have been more careful. When we compare the strength of various sentences that differ in the placement of EXH, we have to be careful about what the alternatives to EXH are. So far as I can tell, the SMH may well still be in the running as a disambiguation criterion, if only we could be sure what the alternatives are in any given experimental setup. Since we don't know this, we can't really be sure whether the SMH has been properly tested.

As mentioned above, we are grateful for reminding us to take into consideration Chemla & Spector's discussion of the SMH in this case. Their footnote 6 makes a similar point to the reviewer's. We acknowledge that Chemla & Spector believe that logical strength may still play a role despite their findings and that this may also extend to our findings in the reflection section 6. However, like Chemla & Spector and the reviewer, we have no strong vision of how this idea could be realized and so must leave it for future work.

> Having said this, **it's still not clear to me that there is any motivation to appeal to the SMH the way the authors do.** Putting aside the issues raised earlier, it is important to note that **the works that the authors cite were all very careful to limit the immediate applicability of the SMH to either reciprocals (Dalrymple et al.) or to plural predication more generally (Winter). One is of course welcome to try extending its applicability, but my reading of the literature is that the SMH was not intended as a general disambiguation principle** (lest it run into well-known issues in other areas, e.g., preferences in scope-ambiguities).

It seems that we have reach rock bottom here, where the reviewer's view differs irresolvably from ours. We consider Chierchia, Fox and Spector (2012) "The Grammatical View of Scalar Implicatures and the Relationship between Semantics and Pragmatics" a great and inspiring paper by great and inspiring minds. This paper suggests to use the SMH for disambiguating parses. Taking great and inspiring papers and minds seriously, we therefore do not think that it is whimsical to pay attention to the SMH, especially, as we stress, our emphasis on it is because it is the only fully spelled out proposal for enriching grammaticalism that applies to our abstract experimental setting.

> C: "Ex ante" predictions: **The authors in many places write that certain proposals are not formulated as "ex ante" predictions. But the predictions of all the theories the authors discuss are all fully predictive: given a sentence and a context, just about every theory of strengthening I know clearly predicts how a scalar sentence will be interpreted.** Of course, in experimental settings many relevant features of the context are left open, and hence participants have to guess what context they're in (see e.g., Crain & Steedman, 1985). This is certainly the case for the author's experiment, in which many of the contextual features that are important for strengthening are unspecified (e.g., relevance, assumptions about the speaker's mental state, etc). But this is a general feature of psycholinguistic studies, is it not? If you leave open crucial contextual features, participants have to guess those values. Does this make the theories any less predictive? Is the difficulty in pinning down a context a difficulty for the theory or for the experimenter?

We are grateful for this comment, because it shows that we have been insufficiently clear on our intended meaning of *ex ante* predictions. We have clarified this in footnote XXX. We are interested in *ex ante* predictions FOR OUR EXPERIMENT, not general predictions *given a set of contextual parameters*.

### 2015-10-16 text/paper/revision_02/paper.tex
revised up to sec 3.3

\begin{abstract}
  The scalar item \emph{some} is widely assumed to receive a meaning
  enrichment to \emph{some but not all} if it occurs in matrix
  position. The question under which circumstances this enrichment can
  occur in certain embedded positions plays an important role in
  deciding how to delineate semantics and pragmatics. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present new experimental data that bear on this theoretical
  issue. In distinction to previous experimental approaches, we
  presented sentence material auditorily in order to explicitly
  control prosodic markedness of the scalar item. Moreover, our
  experiment sheds light on the relative preferences or salience of
  candidate readings. The presented data turn out to be unexpected
  under a traditional Gricean view, but also suggest refinement of the
  more recent grammatical approach.
\end{abstract}

@@

To deal with these methodological problems, this paper presents
results from an experimental study which presented sentence materials
auditorily and explicitly manipulated contrastive stress on embedded
scalar items. We employed an \emph{incremental verification task} in
which parts of a to-be-evaluated picture were hidden and only revealed
piece-wise at the participants’ request until they felt able to give a
binary truth-value judgement \citep[see][]{Conroy2008}. We use both a
classical regression analysis and a Bayesian statistical model to
analyze the data from this novel task, and validate this method by
including control conditions testing ambiguous sentences with a
well-known preference on available readings. We argue that this method
provides categorical behavioral data that is both indicative of the
reading preferences among participants and largely independent of
potential pictorial confounds, such as the mentioned typicality
effects.

@@

\caption{Examples of distinguishing situations for \as-sentences}
  \label{fig:AS-distinguishing-pics}
\end{figure}

@@

There are two main theoretical positions which appear to make
different predictions about the readings of \as- and \es-sentences
\citep[see][for
overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}. We
will refer to these as \emph{traditionalism} and \emph{grammaticalism}
and treat each in turn. Both approaches are addressed here as ``core
theories'' (terminology from
\citeauthor{ChemlaSingh2014:Remarks-on-the-}): two main ideas behind
several approaches to quantity implicatures. To derive from these core theories
\emph{ex ante} falsifiable predictions about
to-be-expected observations in a concrete behavioral experiment,
additional ``auxiliary assumptions'' are necessary, even
irrespective of processing accounts. Here, we spell out a set of such
auxiliary assumptions for each core theory. Our motivation for the
particular choices we make is partly guided by practical concerns, so
as to have a concrete set of predictions for each core theory to
formulate expectations and compare our data to. We therefore introduce
certain relevant variants of either core theory, the predictions of
which are summarized in Table~\ref{tab:predictions} on
page~\pageref{tab:predictions}. How other potential instantiations of
either core theory fare in light of our data will be discussed in
Section~\ref{sec:critical-reflection}.

@@

Traditionalism's predictions about availability and relative salience
of readings of \as- and \es-sentences depend on further auxiliary
assumptions. To have handy labels, we distinguish between strong and
weak, and between restricted and unrestricted variants.

Strong and weak traditionalism differ with respect to whether the
assumptions needed to derive (non-epistemic) implicatures are
plausibly warranted in the given context of utterance (or some
experiment or other). These assumptions include relevance of the
information in question, mutual awareness that the stronger
alternative has been a speaker option, the speaker's competence about
the issue, etc. \emph{Strong traditionalism} assumes that the
additional assumptions needed to derive (non-epistemic) implicatures
are sufficiently salient to prefer an implicature reading over a
literal reading; \emph{weak traditionalism} assumes the reverse
preference order. In other words, in the context of a given
experiment, it is compatible with a traditionalist position to expect
literal or implicature readings to be more prominent. Or, put yet
differently, a traditionalist could be uncertain as to whether a given
experiment is more likely to trigger more implicature readings or
literal readings. Without more information about the experiment or
context of interpretation, traditionalism is compatible with either
salience ordering.

Orthogonal to this, we distinguish restricted and unrestricted
variants of traditionalism. For our purposes, restricted
traditionalism considers only alternative expressions that are
stronger than the to-be-interpreted utterance. Unrestricted
traditionalism also allows alternatives that are derived from
replacing \emph{some} with \emph{all} and vice versa, if necessary
multiple times, even if the resulting alternative is not logically
stronger. Restricted traditionalism considers only \as-sentences to
have a relevant alternative, namely (\ref{bsp:AE-Alternative}). It
then predicts the availability of a global reading for \as-sentences
on top of the literal. Restricted traditionalism predicts only literal
readings of \es-sentences, because the alternative
(\ref{bsp:GE-Alternative}) does not entail the literal reading of
(\ref{bsp:GE}). Every implicature reading available to restricted
traditionalism is also available to unrestricted traditionalism, but
the latter's predictions are even richer. For \as-sentences, the
potential alternative (\ref{bsp:AE-Alternatives-Extended}) also makes
local readings available
\citep[e.g.][]{Sauerland2004:Scalar-Implicat}: conjoining a literal
reading of (\ref{bsp:AE}) with the negation of
(\ref{bsp:AE-Alternatives-Extended}) gives a local reading.

@@

\noindent For \es-sentences, we derive a global reading via the
negation of alternative (\ref{bsp:GE-Alternative}), but not local
readings.

In sum, a traditionalist core theory is compatible with a range of
observations about the availability and relative salience of
implicature readings. These are summarized in
Table~\ref{tab:predictions}. Most importantly for the subsequent
discussion, traditionalism does not predict local readings for
\es-sentences and can favor implicature readings over literal ones or
vice versa.

@@

It is a topic of active current debate as to how a grammaticalist
approach should be supplemented with a general and well-motivated
\emph{disambiguation criterion} so as to rule out unattested readings
obtainable by embedded exhaustification and to make concrete
predictions about preferences over readings made
available. % Grammaticalists therefore
% acknowledge that \emph{some} disambiguation principle must be
% specified, for otherwise grammaticalism would hardly make any
% commitment and would overpredict readings in cases where they are
% unattested, i.e., when scalar items appear in downward-entailing
% contexts \citep[c.f.][for explicit
% discussion]{FoxSpector:Economy-and-Emb}.
Three kinds of approaches have been suggested in the literature
\citep[c.f.][]{ChemlaSingh2014:Remarks-on-the-}. We briefly touch upon
each, but focus on the one that is least controversially applicable to
our experimental case, and that has theoretical significance beyond
the debate about embedded implicatures.

To start with,
\citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
obligatory presence of $\exh(\cdot)$ with variability in the set of
alternatives to feed into each $\exh(\cdot)$. Under this approach,
alternatives may be pruned entirely, so that all occurrences of
$\exh(\cdot)$ become vacuous, resulting in a literal reading. Whether
alternatives apply or not is a matter of their relevance. It is not
clear what his approach predicts \emph{ex ante} about the relative
salience of candidate readings in a neutral experiment that does not
explicitly provide information about which alternatives are relevant
(for whatever purpose). However, we will show in
Section~\ref{sec:critical-reflection} that Magri's approach can be
brought to accommodate the data very well after the fact.

Other proponents of grammaticalism assume that insertion of $\exh(\cdot)$ is
optional. Under one proposal for disambiguation, readings are the more
preferred the better they answer the contextually given question under
discussion (QUD)
\citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. This
is a plausible suggestion, but does not give clear predictions for a
case like our experiment without fixed QUD. Subjects could in
principle accommodate any QUD, so that this approach would not
restrict the space of reading preferences either.

The last kind of disambiguation approach does yield clear predictions
of reading preferences for the case at hand. It selects
readings by comparison of logical strengths, as suggested by the
\emph{strongest meaning hypothesis} of
\citet{DalrympleKanazawa1998:Reciprocal-Expr}. Supplementing
grammaticalism with a strength-based selection criterion has been
suggested, in one form or another, in many contributions to this
paradigm
\citep[e.g.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. At
the same time, the strongest meaning hypothesis has been frequently
called upon for disambiguation purposes in other domains as well,
including reciprocals \citep{DalrympleKanazawa1998:Reciprocal-Expr},
plural predication \citep{Winter2001:Plural-Predicat} or vagueness
\citep{CobrerosEgre2012:Tolerant-Classi}. For these reasons, we focus
from now on this latter type of selection
principle. Section~\ref{sec:critical-reflection} reconsiders
alternative selection principles.

\citet{ChierchiaFox2008:The-Grammatical} discuss two concrete variants
of strength-based disambiguation that make non-trivial predictions
about preferred readings of \as- and \es-sentences (unlike, say, the
more detailed variants of \cite{FoxSpector:Economy-and-Emb}): fix a
sentence with propositional content $S$ and candidate readings $C(S)$,
where $C(S)$ contains $S$ and all readings derivable from inserting
$\exh(\cdot)$ at suitable scope sites;\fn{Strictly speaking, we should
  compare \emph{parses} of sentences with $\exh(\cdot)$ at various
  scope sites with respect to the readings that these parses give rise
  to \citep[see][]{ChierchiaFox2008:The-Grammatical}, but we may
  ignore this detail here for ease of exposition.} then define for
$X,Y \in C(S)$ either
\begin{exe}
\ex \label{bsp:SMH-Total} 
  $X$ is preferred to $Y$ iff $X \subset Y$ 
  \attrib{\citep[(104)]{ChierchiaFox2008:The-Grammatical}}
\end{exe}
or
\begin{exe}
\ex \label{bsp:SMH-Partial}  $X$ is preferred to $Y$ iff $X \subset Y$
  and $X$ and $Y$ are readings obtained from applications of
  $\exh(\cdot)$ at exactly the same scope sites, except for
  one. \attrib{\citep[(105)]{ChierchiaFox2008:The-Grammatical}} 
\end{exe}
Since the former is entailed by the latter, we will speak of
\emph{weak grammaticalism} and \emph{strong grammaticalism},
depending on whether (\ref{bsp:SMH-Total}) or (\ref{bsp:SMH-Partial})
is used.

These two varieties of grammaticalism give rise to different
predictions about preferred readings. The preference for readings that
weak grammaticalism predicts mirrors the entailment relations in
(\ref{bsp:Entailments-AS}) and (\ref{bsp:Entailments-GE}): for
\as-sentences, weak grammaticalism predicts that local readings are
preferred over global readings which in turn are preferred over
literal readings; for \es-sentences weak grammaticalism predicts that
global readings are most preferred, while literal and local readings
are not ranked with respect to preference. Strong grammaticalism, on
the other hand, predicts that \as-sentences preferably get either a
local or a global reading rather than a literal reading, but does not
rank these former two with respect to each other because they differ
in more than one application of the $\exh(\cdot)$ operator. For
\es-sentences, then, strong grammaticalism does not predict \emph{any}
preference relations between candidate readings at all.

\medskip

Taking stock, traditionalism and grammaticalism have been introduced
as fairly general core theories that need backup from particular
auxiliary assumptions to make concrete predictions about availability
and reading preferences for our target sentences. Most notably, under
the assumptions made here, traditionalism does not predict local
readings for \es-sentences to be available while grammaticalism does.
Grammaticalism, in the form proposed by
\citet{ChierchiaFox2008:The-Grammatical}, predicts that all candidate
readings are available and that literal readings are never preferred. All predictions are summarized in
Table~\ref{tab:predictions}.

>>>>

\begin{abstract}
  The scalar item \emph{some} is widely assumed to receive a meaning
  enrichment to \emph{some but not all} if it occurs in matrix
  position. The question under which circumstances this enrichment can
  occur in certain embedded positions plays an important role in
  deciding how to delineate semantics and pragmatics. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present new experimental data that bear on this theoretical issue. In distinction to
  previous experimental approaches, we presented sentence material auditorily in order to
  explicitly control prosodic markedness of the scalar item. Moreover, our experiment sheds
  light on the relative preferences or salience of candidate readings. The presented data turn
  out to be unexpected under a traditional Gricean view, but also challenge the idea that of
  disambiguation by logical strength in grammaticalist approaches.
\end{abstract}

@@

To deal with the problem of ``silent intonation,'' this paper presents results from an
experimental study which presented sentence materials auditorily and explicitly manipulated
contrastive stress on embedded scalar items. To address worries about pictorial ``typicality
effects,'' we employed an \emph{incremental verification task} in which parts of a
to-be-evaluated picture were hidden and only revealed piece-wise at the participants’ request
until they felt able to give a binary truth-value judgement \citep[see][]{Conroy2008}. In order
to obtain information about salience of readings, we use both a classical regression analysis
and a Bayesian statistical model to analyze the data from this novel task, and validate this
method by including control conditions testing ambiguous sentences with a well-known preference
on available readings. % We argue that this method provides categorical behavioral data that is
% both indicative of the reading preferences among participants and largely independent of
% potential pictorial confounds, such as the mentioned typicality effects.

@@

\caption{Examples of distinguishing situations for \as-sentences. The dots on the left
  represent students, the dots on the right papers. An arrow from left to right represents that
  a student has read a paper.}
  \label{fig:AS-distinguishing-pics}
\end{figure}

@@

There are two main theoretical positions which appear to make different predictions about the
readings of \as- and \es-sentences \citep[see][for
overview]{Horn2006:The-Border-Wars,Geurts2010:Quantity-Implic,Sauerland2012:The-Computation,ChemlaSingh2014:Remarks-on-the-}. We
will refer to these as \emph{traditionalism} and \emph{grammaticalism} and treat each in
turn. Both approaches are addressed here as ``core theories'' (terminology from
\citeauthor{ChemlaSingh2014:Remarks-on-the-}): two main ideas behind several approaches to
quantity implicatures. While traditionalism qua ``core theory'' makes some non-trivial
predictions about salience of readings of \as- and \es-sentences, grammaticalism does not. To
derive from grammaticalism a set of falsifiable predictions about outcomes of a concrete
behavioral experiment like ours \emph{ex ante}, i.e., before having seen any data from that
particular experiment, additional ``auxiliary assumptions'' are necessary. Here, we focus on
one such ``auxiliary assumption,'' for reasons to be spelled out
below. Section~\ref{sec:critical-reflection} will revisit grammaticalism as a ``core theory''
\emph{ex post}, i.e., in the light of our data.

@@

Traditionalism's predictions about general availability of reading depend on which alternative
utterances we consider. For \as-sentences, traditionalism can derive the global reading by
assuming (uncontroversially) that (\ref{bsp:AE-Alternative}) is an alternative. It can derive
the local reading by assuming (more controversially) that (\ref{bsp:AE-Alternatives-Extended})
is a relevant alternative \citep[e.g.][]{Sauerland2004:Scalar-Implicat}.\footnote{It is more
  controversial that (\ref{bsp:AE-Alternatives-Extended}) is an alternative to (\ref{bsp:AE}),
  because the former does not entail the latter.}

@@

\noindent For \es-sentences, traditionalism can derive the global reading if we assume
(controversially) that (\ref{bsp:GE-Alternative}) is a relevant alternative. Since local
readings are logically independent of literal readings, there is no way that traditionalism can
derive them from the Gricean recipe, no matter what alternatives we consider.

Traditionalism's predictions about preferences among available readings depend whether the
speaker is (most likely) knowledgeable in the relevant sense. We predict a strong non-epistemic
implicature that a given alternative is false if the speaker is assumed to be competent;
otherwise the preferred reading would be a literal reading or a weak epistemic implicature
(that the speaker does not know whether the alternative is true). In the context of a given
abstract experiment that does not manipulate speaker expertise (like ours), it is then
\emph{prima facie} compatible with a traditionalist position to expect literal or implicature
readings to be more prominent.

In sum, a traditionalist core theory is compatible with a range of observations about the
availability and relative salience of implicature readings. Most importantly for the subsequent
discussion, traditionalism does not predict local readings for \es-sentences and can favor
implicature readings over literal ones or vice versa.

@@

It is a topic of active current debate as to how a grammaticalist
approach should be supplemented with a general and well-motivated
\emph{disambiguation criterion} so as to rule out unattested readings
obtainable by embedded exhaustification and to make concrete
predictions about preferences over readings made
available. % Grammaticalists therefore
% acknowledge that \emph{some} disambiguation principle must be
% specified, for otherwise grammaticalism would hardly make any
% commitment and would overpredict readings in cases where they are
% unattested, i.e., when scalar items appear in downward-entailing
% contexts \citep[c.f.][for explicit
% discussion]{FoxSpector:Economy-and-Emb}.
Several approaches have been suggested in the literature
\citep[c.f.][]{ChemlaSingh2014:Remarks-on-the-}. We focus here on the one that is least
controversially applicable to our experimental case, and that has theoretical significance
beyond the debate about embedded implicatures: disambiguation by comparison of logical
strengths, as suggested by the \emph{strongest meaning hypothesis} of
\citet{DalrympleKanazawa1998:Reciprocal-Expr}.\footnote{We will come back to other
  implementations of grammaticalism in Section~\ref{sec:critical-reflection}.}

% To start with,
% \citet{Magri2009:A-Theory-of-Ind,Magri2011:Another-Argumen} opts for
% obligatory presence of $\exh(\cdot)$ with variability in the set of
% alternatives to feed into each $\exh(\cdot)$. Under this approach,
% alternatives may be pruned entirely, so that all occurrences of
% $\exh(\cdot)$ become vacuous, resulting in a literal reading. Whether
% alternatives apply or not is a matter of their relevance. It is not
% clear what his approach predicts \emph{ex ante} about the relative
% salience of candidate readings in a neutral experiment that does not
% explicitly provide information about which alternatives are relevant
% (for whatever purpose). However, we will show in
% Section~\ref{sec:critical-reflection} that Magri's approach can be
% brought to accommodate the data very well after the fact.

% Other proponents of grammaticalism assume that insertion of $\exh(\cdot)$ is
% optional. Under one proposal for disambiguation, readings are the more
% preferred the better they answer the contextually given question under
% discussion (QUD)
% \citep[e.g.][]{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}. This
% is a plausible suggestion, but does not give clear predictions for a
% case like our experiment without fixed QUD. Subjects could in
% principle accommodate any QUD, so that this approach would not
% restrict the space of reading preferences either.

Supplementing grammaticalism with a strength-based selection criterion has been suggested, in
one form or another, in many contributions to this paradigm
\citep[e.g.][]{FoxSpector:Economy-and-Emb,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Spector2014:Global-Positive}. At
the same time, the strongest meaning hypothesis has been frequently called upon for
disambiguation purposes in other domains as well, including reciprocals
\citep{DalrympleKanazawa1998:Reciprocal-Expr}, plural predication
\citep{Winter2001:Plural-Predicat} or vagueness \citep{CobrerosEgre2012:Tolerant-Classi}. The
main reason, however, why we focus on strength based disambiguation is because it is, as far as
we can say, the only disambiguation mechanism for grammaticalism suggested in the literature
that gives predictions about potential outcomes of our experiment \emph{ex ante}, i.e., before
having seen any data of that experiment.\footnote{See also
  \citet{ChemlaSpector2010:Experimental-Ev} for insightful discussion of strength-based
  disambiguation in the light of their experimental results.}

Most straightforwardly, disambiguation by logical strength predicts that preferences for
readings would just mirro mirror the entailment relations in (\ref{bsp:Entailments-AS}) and
(\ref{bsp:Entailments-GE}): for \as-sentences, weak grammaticalism predicts that local readings
are preferred over global readings which in turn are preferred over literal readings; for
\es-sentences weak grammaticalism predicts that global readings are most preferred, while
literal and local readings are not ranked with respect to
preference.\footnote{\citet{ChierchiaFox2008:The-Grammatical} consider another, more elaborate
  variant of disambiguation based on strongest meanings, but it is not necessary for purposes
  to discuss these details here.}
